Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
update non-tech section

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
“Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
 problem, because it doesn't look so easy.” Richard Feynman’s words are as true today as when he spoke them almost forty years ago.

@@

The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition or simultaneous combination of
both a predetermined ‘0’ and a ‘1’ state. The quantum algorithms were run on superconducting qubits, these are a physical realisation of quantum bits
 based upon what are known as superconducting interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule
 (in this case molecular Hydrogen).

@@

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems in
nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
 hardware and software that will allow for efficient quantum simulations of chemical systems. Dr Abolfazl Bayat of the Controlled
 Quantum Dynamics research group at UCL states that "noise-resilient quantum computers would have transformative effects in many fields, but especially
  in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of tantamount importance in quantum chemistry
 is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
 interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
 testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
 and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.

>>>>

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
``Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
 problem, because it doesn't look so easy.” Richard Feynman’s words are as true today as when he spoke them almost forty years ago.
 And it is this opinion of Feynman among others which prompted the enormous effort that has been expended on the development of quantum computing
 since then. The paper `Scalable Quantum Simulation of Molecular Energies' by O’Malley et al. is evidence of just how far the technology
  has come in this time, and indicates what we might expect from superconducting quantum computing technologies in the future.

@@

The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition, or simultaneous combination, of
both a predetermined `0’ and a `1’ state. In paper by O’Malley et al., the quantum algorithms were run on superconducting qubits. These are a
physical realisation of quantum bits based upon what are known as superconducting quantum interference devices (SQUIDs), and they are used here
to find properties of the wavefunction of molecular Hydrogen.

@@

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for advancing the field of quantum computing was the desire to simulate quantum
 systems in nature through the use of quantum systems, and by so doing to circumvent the exponential computing power needed to do these simulations
 on classical hardware. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum hardware
 and software that will allow for efficient quantum simulations of quantum chemical systems. Dr Abolfazl Bayat, a researcher at the Controlled
 Quantum Dynamics research group at UCL, states that "noise-resilient quantum computers would have transformative effects upon many fields,
 but especially in quantum chemistry where efficient quantum simulations would represent a significant leap forward for the field". A problem of
 tantamount importance in quantum chemistry is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy
 eigenvalues define a great deal of properties of interest in the molecule. This is of great importance in for example the development of
 pharmaceuticals where companies have an extremely laborious testing and trials process, if a significant part of the initial testing process
 could be done in silico - this would represent significant savings and would better ensure that the pharmaceutical under development behaved as
 required prior to starting trials.
